Case study: The corona of an M7 fast rotator with a high latitude flare

### 2023-04-24 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Corona of an M7 fast rotator with a high latitude flare}

@@

@@

    \caption{TIC 277539431 (WISEA J105515.71-735611.3)}
    \begin{tabular}{ll}\hline 
         Parameter & Value  \\\hline
         Distance & $13.70\pm0.11\,$pc [2] \\
         $G$ mag & \\
         $G_{BP}$ mag & \\
         $G_{BP}$ mag & \\
         $K_s$ mag & $9.666 \pm 0.024$ [3]\\
         $J$ mag & $10.630 \pm 0.023$ [3] \\
         SpT & M7 [1]\\
         Rotation period & $273.618 \pm 0.007\,$min [1]\\
         $v\sin i$ & $38.6\pm1.0\,$km/s [1] \\
         Inclination & $87.0^{+2.0}_{-2.4}\,$ deg [1]\\
         Radius & $0.145\pm0.004\,R_\odot$ [1]\\
         TESS flaring rate $\beta$ &  \\\hline

@@

@@

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_onlyflare_data_resid.png}
        \caption{
         No flare PN Double apec spectrum fit.
        }
        \label{fig:spec_pn_noflare}
    \end{centering}
\end{figure}

@@

\section{Discussion}

>>>>

% Title
\title{Case study: The corona of an M7 fast rotator with a high latitude flare}

@@

Age unknown ... \citep{schneider2018hazmat} classify it as field star, but its FUV and NUV fluxes are on the high end for field stars and would be compatible with the NUV/FUV emission from younger open cluster members as well

@@

    \caption{TIC 277539431 (WISEA J105515.71-735611.3)}
    \begin{tabular}{ll}\hline 
         Parameter & Value  \\\hline
         Distance & $13.70\pm0.11\,$pc [2] \\
         $G$ mag & \\
         $G_{BP}$ mag & \\
         $G_{BP}$ mag & \\
         $K_s$ mag & $9.666 \pm 0.024$ [3]\\
         $J$ mag & $10.630 \pm 0.023$ [3] \\
         SpT & M7 [1]\\
         age & \\
         Rotation period & $273.618 \pm 0.007\,$min [1]\\
         $v\sin i$ & $38.6\pm1.0\,$km/s [1] \\
         Inclination & $87.0^{+2.0}_{-2.4}\,$ deg [1]\\
         Radius & $0.145\pm0.004\,R_\odot$ [1]\\
         TESS flaring rate $\beta$ &  \\\hline

@@

From the proposal: $F_X=2.7^{-13}$ erg/s/cm$^2$, $L_X=6\cdot10^27$ erg/s (update with new eROSITA data) -- 1 oom above the measured XMM values.
\begin{table*}
% \movetableright=-20mm
\footnotesize
    \script{TABLE_specfits.py}
    \caption{XSPEC fits to PN, MOS1/MOS2 and joint data also.}
    \input{output/specfit.tex}
        \label{tab:specfit}
\end{table*}

@@

\begin{figure}
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_noflare_data_resid.png}
        \caption{
         No flare PN Double apec spectrum fit.
        }
        \label{fig:spec_pn_noflare}
    \end{centering}
\end{figure}

@@

\section{Discussion}
\citep{pass2022constraints} on rotational evol of late Ms

FFD power law fit converged after 16000 steps on $\alpha = 1.77_{-0.23}^{+0.29}$.

$\log_10(R_{31.5}$, that is, the rate of flares per day with energies above $\log E_{flare}=10^{31.5}\,$erg, is ca. $-0.7$, consistent with other late M dwarfs~\citep{medina2022galactic}.

\begin{figure}
    \script{FIGURE_tess_ffd.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/tess_ffd.png}
        \caption{
         Flare frequency distribution and power law fit.
        }
        \label{fig:ffd}
    \end{centering}
\end{figure}
